Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging

### 2014-03-07 writeup/gz_hubble_data.tex
edits
stuff

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. \label{exampleFERENGI}}
\end{figure*}

@@

We show here the {\bf currently fake} results of citizen scientist classifications of images of galaxies placed at artificial redshifts. Figure \ref{results1} shows the {\bf currently fake} change of vote fractions for the change of $p_{\rm features}$ with redshift, for three galaxies with different vote fraction levels, three surface-brightness levels and 7 evolutionary corrections.

@@

\includegraphics[width=0.35\textwidth,angle=90]{fake_results.ps}

\caption{Fake results of the FERENGI redshifting exercise. For three vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each, we show the evolution of the vote fractions for feature X with redshift.}

@@

KS, KLM, BS, CL thank ASIAA for hosting the ``Citizen Science in Astronomy" workshop at which some of this analysis was done.

>>>>

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{exampleFERENGI}}
\end{figure*}

@@

We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts. Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7 evolutionary corrections (this last bit is indicated by the colour).

@@

\includegraphics[width=0.35\textwidth,angle=90]{somewhat_fake_results.ps}

\caption{Preliminary results of the FERENGI redshifting exercise. WARNING NO USER WEIGHTING.... For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs. smooth with redshift.}

@@

We thank ASIAA for hosting the ``Citizen Science in Astronomy" workshop, Mar 3-7th 2014 in Taipei, Taiwan, at which some of this analysis was done.
